---
title: "LEAP-RE T5.3. | Scientometric Analysis"

output: slidy_presentation
---

```{r setup, include=FALSE}
library(widgetframe)
```

## Completed Steps

- Keyword collection
- Keyword unification (MESRS - ZSI)
- Query optimization
- Accuracy test of the results through sampling 
- Data download, dataset preparation, pre-processing, data cleaning
- Initial data exploration
- Distribution of tasks between partners



## Dataset

- ~ 31.000 publications
- 10 years range (2011-2020)
- Identification RE-related publications: ~80% accuracy

```{r echo=FALSE}
library(canvasXpress)
abs_rel_plt <- readRDS(file = "../../01_data/03_visualisations/abs_rel_plt.Rds")
abs_rel_plt
```

## Further tasks
- Selection of a subset of countries from each region.
- Analysis and visualisation of:
  * Connections between African countries as well as with other regions.
  * Interactions between organisations.
- Report.
```{r echo=FALSE}
afr_cou_plt <- readRDS(file = "../../01_data/03_visualisations/afr_cou_plt.Rds")
afr_cou_plt
```


## Test

- BLANK
- Lorem ipsum

```{r echo=FALSE}
map_pub_freq <- readRDS(file = "../../01_data/03_visualisations/map_pub_freq.Rds")
map_pub_freq
```
