---
title: "LEAP-RE T5.3. | Scientometric Analysis"
output:
  slidy_presentation: default
  beamer_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
library(widgetframe)
library(leaflet)
library(leaflet.providers)
```

## Completed Steps

- Keyword collection
- Keyword unification (MESRS - ZSI)
- Query optimization
- Accuracy test of the results through sampling 
- Data download, dataset preparation, pre-processing, data cleaning
- Initial data exploration
- Distribution of tasks between partners



## Dataset

- ~ 31.000 publications
- 10 years range (2011-2020)
- Identification RE-related publications: ~80% accuracy

```{r echo=FALSE, out.width="100%"}
library(canvasXpress)
abs_rel_plt <- readRDS(file = "../../01_data/03_visualisations/abs_rel_plt.Rds")
abs_rel_plt
```

## Further tasks
- Selection of a subset of countries from each region.
- Analysis and visualisation of:
  * Connections between African countries as well as with other regions.
  * Interactions between organisations.
```{r echo=FALSE, out.width="100%"}
afr_cou_plt <- readRDS(file = "../../01_data/03_visualisations/afr_cou_plt.Rds")
afr_cou_plt
```


## Selection criteria

- Publication output
- Relative growth in the number of pub. 

```{r echo=FALSE, out.width="100%"}
map_cou_reg <- readRDS(file = "../../01_data/03_visualisations/map_cou_reg.Rds")
map_cou_reg
```

## Selection criteria

- Publication output
- Relative growth in the number of pub. 

```{r echo=FALSE, out.width="100%"}
map_pub_freq <- readRDS(file = "../../01_data/03_visualisations/map_pub_freq.Rds")
map_pub_freq
```


## Co-publication and citation networks

- (Interactive) Network presentation
- Report

```{r echo=FALSE, out.width="100%"}

country_chord <- readRDS(file = "../../01_data/03_visualisations/country_chord.Rds")
country_chord
```
