# Results {#results}

Following clarification of  the motivation and methodology of the 
scientometric analysis on the renewable energy (RE) related research in Africa, 
this chapter is dedicated to the presentation of the results under the following
3 sub-chapters:

1. Overall Figures
2. Regional Analysis
3. Domain Analysis

After delivering a general overview on yearly output, the most visible
countries and organisations as well as distribution of scientific domains and
areas in the RE-related publications in African countries between 2011-2020, *Regional
Analysis* focuses on each of the 5 regions (Northern Africa, Western Africa, Central Africa,
Eastern Africa, Southern Africa)[^0301] individually. Analysis of the geographic regions
include:

* Most visible countries.
* Regional, interregional, and intercontinental collaboration networks of all countries in the region.
* Collaboration networks of the academic organisations in *selected countries*[^0302]. 
* Analysis of the most visible research areas and the correlation network of the
keyword/keyword pairs in the RE-related publications of the *selected organisations*[^0303].

*Domain Analysis* approaches RE-related research in Africa from a different perspective
by analysing the publications under the 5 research domains Physical Sciences,
Technology, Life Sciences & Biomedicine, Social Sciences and Arts & Humanities[^0304]. Analysis
of each domain includes:

* Most visible inter-regional/ intercontinental collaborations between academic organisations.
* Most visible and trending keywords/ keyword pairs. 


```{r child="_03.01-overall_numbers.Rmd", echo=FALSE}
```

```{r child="_03.02-regional_analysis.Rmd", echo=FALSE}
```

```{r child="_03.03-domain_analysis.Rmd", echo=FALSE}
```


[^0301]: A list of the countries in each African Union region can
be found under [https://au.int/en/member_states/countryprofiles2](https://au.int/en/member_states/countryprofiles2).

[^0302]: The two deciding factors for the selection were, firstly, the total RE-related 
publication output, and secondly, the relative growth in the number of RE-related publications.

[^0303]: Selection criteria were the same as the criteria for countries.

[^0304]: Web of Science's research area/domain classification can be found under [https://images.webofknowledge.com/images/help/WOS/hp_research_areas_easca.html](https://images.webofknowledge.com/images/help/WOS/hp_research_areas_easca.html). Because of the fewer number of publications, Social Sciences and Arts & Humanities have been analysed together. 