## Regional Analysis
```{r}
# TODO: Remove figure titles
# TODO: Rewrite the following
```

Following the overall figures of the RE-related publications in Africa this sub-chapter introduces geographical regions of Africa to bring the analysis one step further. Focusing on different regions of Africa prevents the over-representation of already more visible countries in terms of publications in general and also enables a detailed analysis for individual countries and organisations.

```{r auregions, echo=FALSE, out.width="100%", fig.cap="African Union Regions"}
au_regions <- readRDS(file = "../../04_visualisation/02_maps/03_results/au_regions.Rds")
au_regions
```
  
Although the most common definition of African geographical regions is the categorization of the [United Nations Statistics Department](https://unstats.un.org/unsd/methodology/m49/) (UNSD), as the Figure \@ref(fig:auregions) shows, this report uses a different categorization, namely [African Union Geographical Regions](https://au.int/en/member_states/countryprofiles2). The reason for this decision solely lies on the more evenly sized regions in AU categorization. 
  
```{r}
# TODO: Change regions to the AU regions
# TODO: Make links appear as foot note
# TODO: Cite the region sources?
```

```{r afrcouplt, echo=FALSE, out.width="100%", fig.cap="Most visible 15 African countries in  RE-related publications between 2011-2020"}
afr_cou_plt <- readRDS(file = "../../04_visualisation/01_bar_graphs/02_regions/afr_cou_plot.Rds")
afr_cou_plt
```

As Figure \@ref(fig:afrcouplt) summarizes, 4 of the most visible African countries in the RE-related publications are from Northern Africa. South Africa has the highest number of publications. Nigeria and Ghana from Western Africa, Ethiopia and Kenya from Eastern Africa are following those 5 countries. Cameroon is the only country from Central Africa that finds a place between the 15 most visible countries.  




```{r child="_03.02.01-northern_africa.Rmd", echo=FALSE}
```


```{r child="_03.02.02-western_central_east_africa.Rmd", echo=FALSE}
```


```{r child="_03.02.03-southern_africa.Rmd", echo=FALSE}
```

