#### Algeria

```{r algeriaorgtable,  fig.show="hold", out.width="0%", fig.cap="Re-related publication output of the most visible Algerian organisations"}
algeria_org_table <- readRDS(file = "../../04_visualisation/04_tables/algeria_org_table.Rds")
algeria_org_table
```

*Renewable Energy Development Center*, Algeria's dedicated institution for RE-related research is the most visible organisation in the country with ~690 publications. However, the number of RE-related publications of the institution is falling after a spike in 2018 with 127 publications. Although the latency in the record entry process in WoS databases might be causing a proportion of the decline, the number of publications in 2020 seems to be less than half of the number in 2018 (54 pub.).   

*Houari Boumediene University of Sciences* is another Algerian institution that publishes RE-related papers consistently. A similar decline in the number of publications like in the case of *Renewable Energy Development Center* can be observed in the publications of *Houari Boumediene University of Sciences* after 2018 (from 75 publications to 44 publications in 2020). *École Nationale Polytechnique d'Oran University*, *Ferhat Abbas of Setif* and the *University of Batna* are other organisations with similar numbers of RE-related publications (259, 241, 239 pub. respectively), each of those has increased their yearly RE-related publication output to ~30. The decline in the number of publications after ~2018 can be observed in all of the most visible 5 organisations of Algeria.

```{r algerianet, echo=FALSE, out.width="100%", fig.cap="Co-publication network in RE-related publications in organisations from Algeria between 2011-2020"}
algeria_net <- readRDS(file = "../../04_visualisation/03_networks/01_outputs/algeria_net.Rds")
algeria_net

```
```{r}
# Links with less than 20 publications have been removed
```

Co-publication network of Algerian organisations mostly gathered around *Renewable Energy Development Center*, the to RE-related research dedicated institution collaborates with a number of other Algerian academic institutions, from which 14 of the collaboration links include close to or over 20 co-publications. The most visible collaborations with *Renewable Energy Development Center* are with *Houari Boumediene University of Sciences* and *École Nationale Polytechnique d'Oran University*, both with an output of over 60 co-publications.

Most of the international collaborators with more than 25 co-publications with Algerian institutions are French, the collaboration between *University of Batna* and *University of Picardy Jules Verne* is the most visible one with 27 co-publications between 2011-2020. *University of Jijel* collaborates often with Italian institutions like *University of Trieste* (23 co-pub.) and *International Centre for Theoretical Physics* (28 co-pub.). Other than that, *University of Hertfordshire* is the only organisation from the UK that has more than 20 RE-related co-publications with an Algerian organisation (*University Ibn Khaldon*) between 2011-2020. 



##### Renewable Energy Development Center 
```{r redecbarline, echo=FALSE, out.width="100%", fig.cap="Absolute and relative growth of the most visible research areas in RE-related publications of Renewable Energy Development Center between 2011-2020"}
redec_barline <- readRDS(file = "../../04_visualisation/01_bar_graphs/02_regions/redec_ra_barline.Rds")

redec_barline
```

The most visible research areas in the RE-related publications of *Renewable Energy Development Center* are *Energy & Fuels* and *Green & Sustainable Science in Technology*. All of the most visible 5 research areas are declining in numbers after 2018 which indicates that there was at least some effect caused by the delayed entry of the publications into the Web of Science databases. However, even after the possibly missing publication from the last years Thermodynamics seems to be becoming one of the consistently visible research areas in the RE-related publications of Renewable Energy Development Center. Environmental Sciences which already included relatively high number of publications in 2011 (11 pub.) is also becoming a consistent area despite having volatile  yearly number of publications  between 2014-2017.

```{r redecgramnetwork, echo=FALSE, out.width="100%", fig.cap="Keyword/keyword pair correlation network in RE-related publications of Renewable Energy Development center"}
redec_ngram_network_plot <- readRDS(file = "../../04_visualisation/06_ngrams/redec_ngram_network_plot.Rds")

redec_ngram_network_plot
```

Keyword/keyword pair correlation network also displays heavily solar energy-related topics. We are seeing that the exploitation of Algerian Sahara for solar energy production is an often reoccurring theme in the publications of *Renewable Energy and Development Center*. Wind energy-related topics are also emphasized in the most visible keyword pairs.

The reason, why water pumping systems are relatively highly correlated with the solar energy keywords is the recent technological advances to build photovoltaic water pumps. Algeria is one of the most active countries in Africa that search for photovoltaic water pumping solutions especially for the isolated sites which are not connected to an electrical grid (see @benghanem2007 ^[The citations are chosen to inform the reader about possibly unfamiliar concepts. Therefore, instead of citing the publications from the very institution (which are often too technical for the purpose of this study), we have decided to seek more informative papers directed to an uninitiated audience.] for further reading).