### Northern Africa 



```{r natable, echo=FALSE, out.width="100%", fig.cap="RE-related publication output in Northern African countries"}
na_table <- readRDS(file = "../../04_visualisation/04_tables/table_test.Rds")
na_table
```

Countries of Northern Africa have collaborated approximately in the half of the 
total number of renewable energy related publications (17116 publications out of 31099).
4 of the 5 most visible African countries in RE-related publications are from the 
northern region; namely Egypt, Algeria, Tunisia and Morocco. As table \@ref(fig:natable) 
presents all of the Northern Africa countries increased their number of RE-related
publications. Although, as discussed in the previous chapter, slight declines in the 
number of publications between 2019-2020 are most likely caused by the delay of 
document entry into the Web of Science databases, Algeria and Tunisia show a 
decline in their number of publications starting 2017 and 2018 respectively. In the
cases of Libya and Mauritania, however, volatility in the number of publications 
is expected as their total publication outputs are relatively lower. Another 
important observation is in the relative growth rates [^3211], Morocco's number of 
RE-related publications in 2020 is approximately 16 times higher the number in 2011. 
This growth rate is not only the highest in Northern Africa but in the whole continent. 

Following the given analysis of RE-related publication outputs in the Northern Africa; 
Egypt, Algeria and Morocco have been chosen for the deeper analysis of the individual countries. 
While Egypt and Algeria hold the highest numbers of RE-related publications in the northern
region, Morocco has been mainly chosen for the high growth rate in the number of publications.



```{r nanet, echo=FALSE, out.width="100%", fig.cap="TEST"}
na_net <- readRDS(file = "../../04_visualisation/03_networks/01_outputs/na_net.Rds")
na_net
```








[^3211]: Relative growth rate value in this report does not indicate a percentage as
it is usually calculated, instead the equation is simply $end\_value/start\_value = growth\_rate$.