## Regional Analysis {#regional-analysis}
```{r}
# TODO: Rewrite the following
```

Following the overall figures of the RE-related publications in Africa, this section introduces the geographical regions of Africa to broaden the analysis further. Focusing on different regions of Africa prevents the over-representation of already relatively more visible countries in terms of publications and also enables a detailed analysis for individual countries and organisations.

```{r auregions, echo=FALSE, out.width="100%", fig.cap="African Union Geographic Regions"}
au_regions <- readRDS(file = "../../04_visualisation/02_maps/03_results/au_regions.Rds")
au_regions
```
 
To determine the African regions, this study uses [African Union Geographical Regions](https://au.int/en/member_states/countryprofiles2) instead of the [United Nations Statistics Department](https://unstats.un.org/unsd/methodology/m49/) (UNSD). A presentation of the African Union regions can be seen in Figure \@ref(fig:auregions).



As Figure \@ref(fig:afrcouplt) summarizes, 4 of the most visible African countries in the RE-related publications are from Northern Africa. South Africa has the highest number of RE-related publications (~6900) between 2011-2020, only other member country of Southern Africa in the most visible 15 countries is Zimbabwe with 230 RE-related publications between 2011-2020. Nigeria, Ghana, Senegal from Western Africa; Ethiopia, Kenya, Tanzania, Uganda from Eastern Africa; and Cameroon, the only country from Central Africa, are among the 15 most visible countries following the most visible 5 countries.
  
```{r}
# TODO: Make links appear as foot note
# TODO: Cite the region sources?
```

```{r afrcouplt, echo=FALSE, out.width="100%", fig.cap="The most visible 15 African countries in  RE-related publications between 2011-2020"}
afr_cou_plt <- readRDS(file = "../../04_visualisation/01_bar_graphs/02_regions/afr_cou_plot.Rds")
afr_cou_plt
```



```{r child="_03.02.01-northern_africa.Rmd", echo=FALSE}
```


```{r child="_03.02.02-western_central_east_africa.Rmd", echo=FALSE}
```


```{r child="_03.02.03-southern_africa.Rmd", echo=FALSE}
```

