#### Morocco

```{r moroccoorgtable,  fig.show="hold", out.width="0%"}
morocco_org_table <- readRDS(file = "../../04_visualisation/04_tables/morocco_org_table.Rds")
morocco_org_table
```
Morocco has the most rapidly growing number of publications in the 15 most visible African countries in RE-related publications with having 543 publications in 2020 in comparison with 34 RE-related publications in 2011. The same pattern is also observable in the publications of Moroccan Institutions. Each one of the RE-wise most visible 5 organisations in Morocco had 1 digit RE-related publications in 2011 and each of those have published at least ~8 folds of those numbers in 2020. 

*Mohamed V University* is the most visible Moroccan institution in the RE-related publications with 667 publications in total. There is a slight decline in the number of publications after 2018 but the university still collaborates in over 100 RE-related publications yearly. *Mohamed V* and *Mohamed I Universities* are both publishing in comparison with 2011 ~25 times more in RE-related topics.

*University of Sfax*, *University of Casablanca* and *Cadi Ayyad University* are most visible 2., 3. and 4. organisations respectively 


```{r morocconet, echo=FALSE, out.width="100%", fig.cap="Co-publication network in RE-related publications in organisaitons from Morocco between 2011-2020"}
morocco_net <- readRDS(file = "../../04_visualisation/03_networks/01_outputs/morocco_net.Rds")
morocco_net

```
```{r}
# Links with less than 20 publications have been removed
```

Moroccan organisations are interconnected in the RE-related publications with only a few collaborations with an output of more than 25 co-publications. Although *Mohamed V Uni.* has a central position the native collaboration is relatively uniform distributed. 

International collaborations includes mostly French institutions like *Uni. of Lorraine*, *Uni. of Montpellier* and *University of Pau and Pays de l'Adour*.


##### Mohammed V University
```{r mohambarline, echo=FALSE, out.width="100%", fig.cap="TEST"}
moham_barline <- readRDS(file = "../../04_visualisation/01_bar_graphs/02_regions/moham_ra_barline.Rds")

moham_barline
```

