## Overall Figures {#overall-figures}

```{r, include=FALSE}
# Addition: In order to put numbers
# in perspective, the number of publications in the EU-27 countries has been added analysed
# as well.
# TODO: Add EU-27 absolute numbers and relative growth 

# TODO: Add global partners as tree map like here? https://www.canvasxpress.org/examples/treemap-1.html
```


```{r puboty, echo=FALSE, out.width="100%", out.height="50%", fig.cap="Number of RE-related publications in African countries over the years between 2011-2020"}
abs_rel_plt <- readRDS(file = "../../01_data/03_visualisations/abs_rel_plt.Rds")
abs_rel_plt
```


African countries have collaborated in approximately 31k renewable energy (RE) related publications in the 10 years range between 2011-2020. The number of those publications has been constantly
increasing until 2019. Slightly declining publication numbers between 2019
and 2020 (see Figure \@ref(fig:puboty))
is likely caused by the latency in the database entries [^1] according to the explanation of Web of Science. Even after including the 
possibly incomplete amount of publications in 2020, the number of RE-related publications from 
the African countries in total increases from ~1.1k in 2011 to ~4.8k in 
2020 which is an increment by factor ~4.2.  

```{r}
# TODO: Research Areas?
```


```{r choropleth, echo=FALSE, out.width="100%", fig.cap="Total number of RE-related publications in African countries between 2011-2020"}
map_pub_freq <- readRDS(file = "../../04_visualisation/02_maps/03_results/choropleth.Rds")
map_pub_freq
```

```{r}
# TODO: Edit the following text
```

As Figure \@ref(fig:choropleth) shows, South Africa and Egypt are the most visible countries with 6.8k and 6.6k RE-related publications respectively. 20 African countries stay under 40 RE-related
publications in total between 2011-2020. The most visible countries are distributed diversely on the continent, however, other than the Northern African countries and South Africa only Nigeria contributed to over 1000 RE-related publications (2252 pub.) between 2011-2020.  

Although total publication output is a strong indicator of the most visible countries, it does not show the growth rate in the numbers. African countries that show a high increment rate in the number of publications despite having a relatively lower total amount of publications will be analysed in the following chapter.
  




```{r orgmv, echo=FALSE, out.width="100%", fig.cap="Most visible 15 African countries in RE-related publications between 2011-2020"}
org_mv <- readRDS(file = "../../04_visualisation/01_bar_graphs/01_overall_figures/org_mv_barplot.Rds")
org_mv
```

4 of the most visible 5 organisations (*University of Kwazulu-Natal*, *University of Cape Town*, *Stellenbosch University*, and *University of Pretoria*) in RE-related publications are located in South Africa. Each of them has close to or over 800 publications between 2011-2020, Cairo University from Egypt is following them with ~780 publications. 4 other Egyptian institutions; namely Ain Shams University, Tanta University, National Research Centre of Egypt and Alexandria University are also among the 15 most visible organisations. 

*Tunis El Manar University* and the *University of Sfax* from Tunisia are also in the most visible 15 organisations with ~650 and ~550 RE-related publications and *Mohamed V University*, the only organisation from Morocco in the list has ~670 RE-related publications.

Although most of the visible organisations are in general universities, the only organisation from Algeria in the most visible 15 organisations, namely *Renewable Energy Development Center* is an institution completely dedicated to RE-related research. The total number of RE-related publications of *Renewable Energy Development Center* is ~700 between 2011-2020.




```{r resareas, include=FALSE, out.width="100%", fig.cap="Most visible 15 research areas in RE-related publications between 2011-2020"}
## res_mv <- readRDS(file = "../../04_visualisation/01_bar_graphs/01_overall_figures/res_areas_barplot.Rds")
## res_mv
```


```{r resdomains, echo=FALSE, fig.cap="Distribution of research domains in RE-related publications of African countries between 2011-2020"}
## res_domains_pie <- readRDS(file = "../../04_visualisation/05_treemaps/res_domains_pie.Rds")
## res_domains_pie 
gen_ra_sun <- readRDS("../../04_visualisation/05_treemaps/gen_ra_sun.Rds")
gen_ra_sun
```
[^2]

Over 50% of the RE-related publications are associated with research areas from the *Technology* domain. *Energy & Fuels* is the most visible research area in total followed by *Electrical & Electronic Engineering*. Other Engineering fields like *Chemical, Environmental, Mechanical Engineering* are also among the visible research areas. Multidisciplinary discipline *Green & Sustainable Science & Technology* is the 3. most visible research area in total. 

Life Science & Biomedicine and Physical Sciences have a similar number of publications (~8800 pub. both). *Environmental Science* and *Ecology* from Life Sciences & Biomedicine as well as *Multidisciplinary Materials Science* and *Thermodynamics* from Physical Sciences are also in the 10 most visible research areas.

Social Sciences (1325 pub.) is also not absent in the RE-related publications of African organisations. *Environmental Studies* is the most visible research area in this domain with 663 publications.

The 5. research domain Arts & Humanities include only 45 publications, therefore, this domain will be analysed together with Social Sciences in Chapter \@ref(domain-analysis) Domain Analysis.



```{r resareas2, include=FALSE, out.width="100%", fig.cap="Most visible research areas"}
test_res_areas_bar_line <- readRDS(file = "../../04_visualisation/01_bar_graphs/01_overall_figures/test_res_areas_bar_line.Rds")
test_res_areas_bar_line
```



[^1]: As the Web of Science support service informs, it might take up to 2 years for a document to be entered into the Web of Science databases.

[^2]: A single publication may be associated with multiple research domains/ areas. The sum of the number of publications in individual research domains/areas does not add up to the total number of publications.