## Regional Analysis
```{r}
# TODO: Remove figure titles
# TODO: Rewrite the following
```

Following the overall figures of the RE-related publications in Africa this sub-chapter introduces geographical regions of Africa to bring the analysis one step further. 

Focusing on different regions of Africa prevents the over representation of already more visible countries in terms of publications in general and also enables a

```{r auregions, echo=FALSE, out.width="100%", fig.cap="test"}
au_regions <- readRDS(file = "../../04_visualisation/02_maps/03_results/au_regions.Rds")
au_regions
```
  
Although the most common definition of African geographical regions is the categorization of the [United Nations Statistics Department](https://unstats.un.org/unsd/methodology/m49/) (UNSD), as the Figure \@ref(fig:auregions) shows, this research uses a different categorization, namely [African Union Geographical Regions](https://au.int/en/member_states/countryprofiles2). The reason for this decision solely lies on the more evenly sized regions in AU categorization. 
  
```{r}
# TODO: Change regions to the AU regions
# TODO: Make links appear as foot note
# TODO: Cite the region sources?
```

```{r echo=FALSE, out.width="100%"}
afr_cou_plt <- readRDS(file = "../../01_data/03_visualisations/afr_cou_plt.Rds")
afr_cou_plt
```



```{r child="_03.02.01-northern_africa.Rmd", echo=FALSE}
```
