### Northern Africa 



```{r tables-natable, echo=FALSE, out.width="100%", fig.cap="RE-related publication output in the most visible Northern African countries"}
na_table <- readRDS(file = "../../04_visualisation/04_tables/na_table.Rds")
na_table
```

Member countries of Northern Africa have collaborated approximately in half of
the total number of all RE-related publications (17116 publications out of 31099) in Africa between 2011-2020. 4 of the 5 most visible African countries in RE-related publications are from the 
northern region; namely Egypt, Algeria, Tunisia and Morocco. 

As Table \@ref(fig:tables-natable) 
presents, all of the Northern Africa countries increased their number of RE-related
publications until 2017. Although, as discussed in the previous chapter, slight declines in the number of publications between 2019-2020 are most likely caused by the delay of document entry into the Web of Science databases, Algeria and Tunisia show an earlier start of 
the decline in their number of publications starting in 2017 and 2018 respectively. In the
case of Libya, however, volatility in the number of publications 
is expected as their total publication outputs are relatively lower. 

Another important observation is in the relative growth rates [^3211], Morocco's number of 
RE-related publications in 2020 are approximately 16 times higher than the number in 2011. 
This growth rate is not only the highest in Northern Africa but in the whole continent among the most visible countries in RE-related research. 




```{r nanet, echo=FALSE, out.width="100%", fig.cap="Co-publication network of Northern African countries in RE-related publications between 2011-2020"}
na_net <- readRDS(file = "../../04_visualisation/03_networks/01_outputs/na_net.Rds")
na_net
```
```{r}
# links with fewer than 25 publications have been removed
```

RE-related co-publications of the Northern African countries show a rich international network but the collaboration with other African regions seems to be relatively less dense. Only African countries from other regions which have co-published over 25 RE-related papers with Northern African countries are South Africa (28 pub.) and Nigeria (26 pub.). 

Egypt, the most visible country in Northern Africa in terms of RE-related publications,  plays a central role in the network with ~6.6k publications in total. The relatively uniform distributed co-publication network of Egypt includes over 10 EU-27 countries as well as a number of countries from other regions of the world like the USA, China, India, United Kingdom. Egypt's strongest link in the co-publications, however, is with organisations from Saudi Arabia. 

Tunisia, Algeria and Morocco have relatively high numbers of collaborations with French organisations with 751, 881 and 601 co-publications respectively. France in general is the most visible EU-27 country in the RE-related co-publications with African countries. Out of France's ~3250 RE-related co-publications with African countries ~2350 of those have been published with the collaboration of Northern African countries whereas Algeria and Tunisia being the most visible Northern African countries in those collaborations. The closest following EU-27 country in terms of RE-related co-publications is Spain (~580 out of ~820 co-publications with African countries) and Germany (~490 out of 1334 co-publications with African countries).

The 4 mentioned Northern African countries so far, Egypt, Algeria, Tunisia and Morocco are co-publication-wise relatively well interconnected, however, Libya stays out of the co-publication cluster in Northern Africa, from Libya's 233 RE-related publications in the last 10 years none of the Northern African countries had over 25 co-publications with Libya. Instead, Libya's most visible collaborators are United Kingdom (38 co-pub.) and Malaysia (29 co-pub.).

Following the given analysis of RE-related publication outputs in Northern Africa; 
Egypt, Algeria and Morocco have been chosen for the deeper analysis of the individual countries. 
While Egypt and Algeria hold the highest numbers of RE-related publications in the northern
region, Morocco has been mainly chosen for the high growth rate in the number of publications.





[^3211]: Relative growth rate value in this report does not indicate a percentage as
it is usually calculated, instead the equation is simply $end\_value/start\_value = growth\_rate$.




```{r child="_03.02.01.01-egypt.Rmd", echo=FALSE}
```

```{r child="_03.02.01.02-algeria.Rmd", echo=FALSE}
```
```{r child="_03.02.01.03-morocco.Rmd", echo=FALSE}
```
