#### Egypt

```{r egyptorgtable,  fig.show="hold", out.width="0%", fig.cap="Re-related publication output of the most visible Egyptian organisations"}
egypt_org_table <- readRDS(file = "../../04_visualisation/04_tables/egypt_org_table.Rds")
egypt_org_table
```

The most visible Egyptian organisation in the RE-related publications is *Cairo University* with a total of 779 publications between 2011-2020. All of the most visible 5 organisations of Egypt display a fairly linear growth in the number of RE-related publications. However, Ain Shams University and Tanta University show a stagnation between 2019-2020 which might be caused by the delay of document entries into the Web of Science system as mentioned above. Furthermore, Tanta University, which had yearly fewer than 50 RE-related publications until 2016, published in 2019 and 2020 ~125 RE-related papers, this is a growth rate of ~14 fold with respect to the 9 publications in 2011. 

```{r egyptnet, echo=FALSE, out.width="100%", fig.cap="Co-publication network in RE-related publications in organisations from Egypt between 2011-2020"}
egypt_net <- readRDS(file = "../../04_visualisation/03_networks/01_outputs/egypt_net.Rds")
egypt_net

```
```{r}
# Links with less than 20 publications have been removed
```


The Co-publication network of Egyptian organisations shows a relatively dense collaboration structure between *Cairo University*, *Ain Shams University* and *National Research Centre* of Egpyt. *National Research Centre* has over 50 co-publications with each of the other universities in that cluster. *Cairo University* is also in the centre of other 4 Egyptian organisations; namely *Suez Canal Uni.*, *British Uni. in Egypt*, *Zewail City of Sci. Tech* and *American Uni. in Cairo*, with over 20 co-publications each.  

Other visible collaboration links are between *Minia* and *Aswan Universities* with over 50 publications and between *Tanta* and *Kafrelsheikh Universities* with over 70 publications together.  In general, collaborations with organisations from Saudi Arabia are highly visible in the network, especially *King Saud University* is a central node in the network with ~400 RE-related co-publications with Egyptian organisations. 

Other than that, East Asian organisations also have a visible presence in the co-publication network of Egypt. *Tanta University*'s collaborations with Chinese Institutions *Jiangsu Uni.* and *Huazhong Uni* include 60  and 40 co-publications respectively. Several Japanese universities have collaborations with *Aswan University*, *Zagazig University*, *Assiut University*, *Suez University*, *Egypt Japan University* and *Minia University* with over 20 co-publications each. *Minia University*'s collaboration with South Korean institution *JeonBuk National University* also includes 60 RE-related co-publications between 2011-2020.

Visible organisations from EU-27 countries are *Université Bourgogne Franche-Comté* of France (over 25 co-publications with *Zagazig University*), *Ruhr University Bochum* from Germany (22 co-publications with *Mansoura Uni.*), *Budapest University of Technology and Economics* from Hungary and the *University of Jaen* from Spain (both over 25 co-pub. with *Aswan University*).

##### Cairo University

```{r cairobarline, echo=FALSE, out.width="100%", fig.cap="Absolute and relative growth of the most visible research areas in RE-related publications of Cairo University between 2011-2020"}
cairo_barline <- readRDS(file = "../../04_visualisation/01_bar_graphs/02_regions/cairo_ra_barline.Rds")

cairo_barline
```

Looking into the most visible research areas of *Cairo University*, out of 779 publications in total, the most visible research areas are aligning with the most visible research areas in RE-related publications from African countries in general. *Energy & Fuels*, as well as *Electrical & Electronic Engineering* are the most visible research areas in Cairo university, however, the number of RE-related in those areas are not growing in the last years. After the spike in 2017 with ~50 publications, the number of publications from *Energy & Fuels* has fallen to ~30 publications in 2019 and 2020. *Green & Sustainable Science & Technology* and *Environmental Sciences* on the other hand display relatively steady growth in numbers. Considering there was only 1 from each area in 2011,  ~20 RE-related publications in 2020 makes those the fastest growing research areas in the RE-related publications of Cairo University.


```{r cairongramnetwork, echo=FALSE, out.width="100%", fig.cap="Keyword/keyword pair correlation network in RE-related publications of Cairo University"}
cairo_ngram_network_plot <- readRDS(file = "../../04_visualisation/06_ngrams/cairo_ngram_network_plot.Rds")

cairo_ngram_network_plot
```

Figure \@ref(fig:cairongramnetwork) displays the correlation network between the most common keywords and keyword pairs in the RE-related publications of *Cairo University*. As the clusters on the network graph indicate, there is a strong emphasis on solar energy, photovoltaic systems related keywords in *Cairo University*'s publications which is widely the case in African countries. In relation, substances and technologies aiming to improve the efficiency of the effectiveness of solar cells like formic acid, MPPT (Maximum Power Point Tracking, an algorithmic DC-DC converter that increases the efficiency of photovoltaic cells) are also among the visible keyword pairs. Other clusters include wind energy-related keywords as well as biogas/biomass related keywords. The approaches like electrocatalysis that aims to increase the output of solar and wind energy are also often mentioned in the RE-related publications of *Cairo University*.