--- 
title: "LEAP-RE T5.3. | Scientometric Analysis of Renewable Energy Research in Africa"
author: ""
date: "`r Sys.Date()`"
output:
  word_document: default
  pdf_document: default
documentclass: book
header-includes:
  - \let\oldhref\href 
  - \renewcommand{\href}[2]{#2\footnote{\url{#1}}}
bibliography:
- book.bib
- packages.bib
biblio-style: apalike
link-citations: yes
description: This is a minimal example of using the bookdown package to write a book.
  The output format for this example is bookdown::gitbook.
site: bookdown::bookdown_site
---

```{r setup, include=FALSE}
# All the r libraries needed for the document
library(widgetframe)
library(leaflet)
library(leaflet.providers)
library(htmlwidgets)
library(htmltools)
library(canvasXpress)
library(leaflet)
library(leaflet.providers)
library(formattable)
library(sparkline)
library(formattable)
library(tidyr)
library(data.table)
library(htmltools)
```

# Preface {-}

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
