---
title: "LEAP-RE T5.3. | Scientometric Analysis"
subtitle: "Report Outline"
output:
  slidy_presentation: default
---

```{r setup, include=FALSE}
library(widgetframe)
library(leaflet)
library(leaflet.providers)
library(htmlwidgets)
library(htmltools)
library(canvasXpress)
library(leaflet)
library(leaflet.providers)
library(formattable)
library(sparkline)
library(formattable)
library(tidyr)
library(data.table)
library(htmltools)
```

## Main focus points

* Overall Figures
* Regional Analysis
* Research Domain Analysis

```{r mvorg, echo=FALSE, out.width="100%"}
## res_domains_pie <- readRDS(file = "../../04_visualisation/05_treemaps/res_domains_pie.Rds")
## res_domains_pie 
org_mv <- readRDS("../04_visualisation/01_bar_graphs/01_overall_figures/org_mv_barplot.Rds")
org_mv
```
## Overall Figures

- Number of RE-related publications over the years
- Most visible countries & organisations
- Distribution of research areas & domains
```{r resdomains, echo=FALSE, out.width="100%"}
## res_domains_pie <- readRDS(file = "../../04_visualisation/05_treemaps/res_domains_pie.Rds")
## res_domains_pie 
gen_ra_sun <- readRDS("../04_visualisation/05_treemaps/gen_ra_sun.Rds")
gen_ra_sun
```


## Regional Analysis

- Individual analysis of AU regions (Northern, Western, Central, Eastern, Southern Africa)
- Absolute and relative growth in RE-related publications of
  - Most visible countries in each region
  - Most visible organisations in selected countries
- Co-publication networks of countries and organisations 
- Distribution of research areas and
- co-occurrence network of keywords/ keyword pairs in the pub. of selected countries

```{r nanet, echo=FALSE, out.height="10%"}
wa_net <- readRDS(file = "../04_visualisation/03_networks/01_outputs/wa_net.Rds")
wa_net
```

## Domain Analysis
- Most visible international/ inter-regional collaborations in each research domain
- Most visible keywords/ keyword pairs
- Analysis of the most visible keyword and keyword pairs over the years


```{r pstable, echo=FALSE, warning=FALSE, out.width="100%"}
ps_oty <- readRDS(file = "../04_visualisation/06_ngrams/ps_domain_lineplot.Rds")
ps_oty
```

## Output
- Output formats: HTML-doc, PDF-doc and a dashboard
- Dataset and the code are available


```{r redecbarline, echo=FALSE, out.width="60%", fig.cap="Cairo University | Most visible research areas in RE-related publications between 2011-2020"}
cairo_barline <- readRDS(file = "../04_visualisation/01_bar_graphs/02_regions/cairo_ra_barline.Rds")

cairo_barline
```




