---
title: "LEAP-RE T5.3. | Scientometric Analysis"
subtitle: "Results"
output:
  slidy_presentation: default
---

```{r setup, include=FALSE}
library(widgetframe)
library(leaflet)
library(leaflet.providers)
library(htmlwidgets)
library(htmltools)
library(canvasXpress)
library(leaflet)
library(leaflet.providers)
library(formattable)
library(sparkline)
library(formattable)
library(tidyr)
library(data.table)
library(htmltools)
```

## Overall Figures

- Number of RE-related publications over the years
- Most visible countries & organisations
- Distribution of research areas & domains
```{r resdomains, echo=FALSE, out.width="100%"}
## res_domains_pie <- readRDS(file = "../../04_visualisation/05_treemaps/res_domains_pie.Rds")
## res_domains_pie 
gen_ra_sun <- readRDS("../04_visualisation/05_treemaps/gen_ra_sun.Rds")
gen_ra_sun
```


## Regional Analysis

- Individual analysis of AU regions (Northern, Western, Central, Eastern, Southern Africa)
- Absolute and relative growth in RE-related publications of
  - Most visible countries in each region
  - Most visible organisations in selected countries
- Co-publication networks of countries and organisations 


```{r nanet, echo=FALSE, out.height="10%"}
wa_net <- readRDS(file = "../04_visualisation/03_networks/01_outputs/wa_net.Rds")
wa_net
```

## Further Focus & Output
- Co-occurence network in individual research domains
- Trending research areas in selected organisations between 2011-2020
- Output formats: HTML-doc, PDF-doc and dashboard

```{r redecbarline, echo=FALSE, out.width="60%", fig.cap="Renewable Energy Development Center | Most visible research areas in RE-related publications between 2011-2020"}
redec_barline <- readRDS(file = "../04_visualisation/01_bar_graphs/02_regions/redec_ra_barline.Rds")

redec_barline
```




